Seeing Double: Indications From {\it TESS} and {\it Gaia} That PTFO$\,$8-8695b is Not a Planet

### 2020-04-17 paper/ms.tex
made sick posterior table

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded long and short-period signals.}
		{\it Top}: Long-period signal, as in Figure~\ref{fig:splitsignal}.
		{\it Bottom}: Short-period signal. The reference phase is set to the
		``planetary'' dip.  Gray points are the 10 minute cadence
		\texttt{PDCSAP} flux.  Black points are binned to 100 points per
		period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

\input{model_comparison_table.tex}
%\input{model_posterior_table.tex}

We considered nine models, with the number of harmonics per frequency
$N$ and $M$ ranging from one to three.  To select our preferred model,
we used the Bayesian information criterion
(Table~\ref{tab:modelcompare}).  The model with the lowest BIC had
two harmonics at the short 11.74$\,$hr period, and two harmonics
at the long 11.96$\,$hr period.  All of the models have reduced
$\chi^2$ ranging between 1.37 and 1.51, which suggests a plausible
though imperfect agreement between the data and models.

@@

\subsection{Short period dip}
The dip lasts about 45 minutes, and seems to re-occur every 11.74
hours
(Figures~\ref{fig:splitsignal},~\ref{fig:splitsignalii},~\ref{fig:phasefold}).
The dip duration is roughly the same as that observed by previous
investigators \citep{van_eyken_ptf_2012,yu_tests_2015}
The dip depth is comparable to what has been observed in red visual
bands...
%TODO: and how does it compare to IR? bigger or smaller? cite relevant
%studies.

@@

%\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded long and short-period signals.}
		{\it Top}: Long-period signal, as in Figure~\ref{fig:splitsignal}.
		{\it Bottom}: Short-period signal. The reference phase is set to the
		``planetary'' dip.  Gray points are the 10 minute cadence
		\texttt{PDCSAP} flux.  Black points are binned to 100 points per
		period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

We considered nine models, with the number of harmonics per frequency
$N$ and $M$ ranging from one to three.  To select our preferred model,
we used the Bayesian information criterion
(Table~\ref{tab:modelcompare}).  The model with the lowest BIC had
two harmonics at the short 10.74$\,$hr period, and two harmonics
at the long 11.96$\,$hr period.  All of the models have reduced
$\chi^2$ ranging between 1.37 and 1.51, which suggests a plausible
though imperfect agreement between the data and models.

@@

\subsection{Short period dip}
The dip lasts about 45 minutes, and seems to re-occur every 10.74
hours
(Figures~\ref{fig:splitsignal},~\ref{fig:splitsignalii},~\ref{fig:phasefold}).
The dip duration is roughly the same as that observed by previous
investigators \citep{van_eyken_ptf_2012,yu_tests_2015}
The dip depth is comparable to what has been observed in red visual
bands...
%TODO: and how does it compare to IR? bigger or smaller? cite relevant
%studies.

@@

\clearpage
\input{model_comparison_table.tex}
\input{model_posterior_table.tex}
\clearpage

\bibliographystyle{yahapj}                            
\bibliography{bibliography}
